Ensemble Super-Learning for State Estimation. \\Application to the reconstruction of urban pollution.

### 2023-09-08 paper/main.tex
Merge with overleaf

% Math environments for theorems, lemmas, etc.
%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\verify}[1]{{\color{blue} Verify: #1}}
\newcommand{\ascomment}[1]{{\color{teal} Agus: #1}}
\newcommand{\asmodif}[2]{{\color{teal} #1} {\sout{#2}}}

@@

% Comments
\newcommand{\om}[1]{\textcolor{blue}{#1}}
% \newcommand{\om}[1]{#1}

@@

Assuming that all the available information is given by an element $x$ from some abstract metric space $\cX$, and that $u$ belongs to some Banach space $V$ (of potentially infinite dimension, and with associated norm $\Vert\cdot\Vert$), our goal is thus to build a mapping $A:\cX\to V$ such that $A(x)$ approximates $u$ at best in the sense that $\Vert u - A(x)\Vert$ is as small as possible. Ideally, this has to hold for all possible configurations of the system. As we explain later on through mathematical formulas, building such an optimal map is not feasible in practice, so one is inevitably led to consider suboptimal maps $A$. In fact, it is often possible to resort to different techniques to build different reconstruction maps, \asmodif{each of them with its own virtues and drawbacks}{it is generally difficult to rigorously compare their respective quality}. This lead us to propose an approach based on ensemble super-learning in which the different reconstruction mappings do not directly compete against each other (see, e.g., \cite{Breiman1996, LPH2007, PL2010} for general references on super-learning). Instead, we make them collaborate with each other to enhance their respective strengths, and cope for their weaknesses.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pollution as a guiding example}
There are numerous applications in which one is confronted with the above state estimation problem. As a guiding example, we consider throught the paper the real-time reconstruction of urban pollution fields. Beyond the relevance of such a task to limit environmental and health risks in the city, pollution state estimation is an excellent example where collaborative, super-learning methods are required. This is because the problem accumulates several difficulties that make the reconstruction challenging for most common reconstruction methods. Among the issues, we may mention:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Contributions and layout of the paper}
\paragraph{Contributions:} Our main contributions are (i) the construction of a very general ensemble super-learning method for real-time state estimation, (ii) the application to a non trivial example for urban pollution reconstruction and \asmodif{(iii) the construction of a dataset comprised of traffic Google Maps Screenshots that can be used for future studies and developements}. In our numerical experiments, we work with the inner city of Paris, which is a surface covering around $140\,\textrm{km}^2$. The pollutant that we consider is $\textrm{NO}_2$, mainly produced by vehicle emissions. We use real data from sensor measurements \footnote{Data has been extracted from Airparif database that can be found in  \url{https://data-airparif-asso.opendata.arcgis.com}.}, and traffic data from Google Maps. Compared to previous contributions and other existing reconstruction methods (see, e.g., \cite{MSM2009, TMPPB2013}), the use of such traffic data is rather novel. It gives a rough estimation of the spatial density of street traffic. This level of detail is in contrast to many existing approaches which only use time averages of traffic data. Another distinctive point of our approach is the use of graph descriptions of the city instead of working on a spatial domain of $\bR^2$ or $\bR^3$. This allows us to cope with large spatial domains, and also to define physical models through \emph{quantum graphs}, i.e., metric graphs  endowed with a differential operator acting on functions from a certain space (see \cite{BK2013} for details and references). The metric graph structure allows us to take the shape of the city into account, while the definition of differential operators enables to physically model the phenomenon of pollutant dispersion through the streets. It also leads to the definition of suitable and natural functional spaces to pose the problem. Of course, several physical models of different complexity could be considered. In this paper, we work with simple elliptic operators but the model could be refined by considering, for instance, advection-diffusion operators. %Despite the fact that we focus on urban air pollution, the main ideas of the strategy are general, in the sense that they can be taken as guidelines to adress other problems that can be modeled via quantum graphs.

@@

We assume that, from the unknown pollution field $u$, we are only given partial information which we will denote as $x$ (or $x_u$ whenever we will need to emphasize the connection between $x$ and $u$). The data $x$ belongs to a metric space $\cX$, and it may contain several types of information about $u$ that can be of different nature (e.g., local sensor measurements and indirect information such as traffic or weather conditions). Assuming that $u$ belongs to a function space $V$ on the graph $\G$, our goal is to build a mapping
\begin{align*}
A: \cX &\to V \\
x &\mapsto A(x)
\end{align*}
such that, given $x_u\in \cX$, $A(x_u)$ approximates at best the true (unknown) $u$.

@@

We have worked with $m=\perplexityinsert{numstations}$ sensors functioning in the region of interest. As already brought up, their locations do not exactly match with the topology of the metric graph, therefore we project the position to the nearest node on the graph in a pre-processing step. This yields the observational nodes $\vv^\obs$ and coordinates $r^\obs$. As Figure \ref{fig:paris-stations} illustrates, the projected locations are very close \asmodif{(the maximal discrepancy is $\perplexityinsert{MinDistNodeStation}$m, see \cref{fig:correlation})}{} to the exact locations given the global scale of the graph. %Note however that the stations are originally located at different altitudes and since our graph is embedded only in $\bR^2$, we are not taking the effects of altitude into account.

@@

      \item \textbf{Raw data:} \asmodif{we made a script using Selenium python library to automatically take screenshots of Paris\footnote{We tried in a first attempt to use the Google Maps Platform but as it required payment after one week of use we decided to code our own pipeline.} every $\perplexityinsert{screenshotperiod}$ minutes over an area of $\perplexityinsert{screenshotwidth} \times \perplexityinsert{screenshotheight}$ pixels with zoom $\perplexityinsert{zoom}$. An example of the raw  \textit{image} can be seen in \cref{fig:traffic-raw-data}. Note that city landmarks could not be removed before taking the screenshot neither by substracting a background image as each screenshot has slight variations rendering this approach impractical. Another issue is the absence of traffic data in the inner streets of the city. 

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Reconstruction benchmarks}
Our approach to reconstruct an unknown pollution field $u\in V$ from the partial data $x_u\in \cX$ is based on a supervised learning strategy involving super-learners. We thus assume that we have a database of $T$ observations, one for each time,
$$
X_T = \{x_1,\dots, x_T\} \subset \cX,
$$
each $x_T$ corresponding to partial observations of an unknown pollution field $u_k$ that took place in the past. Our goal is to use the database to build a reconstruction map
\begin{align*}
A: \cX &\to V \\
x &\mapsto A(x)
\end{align*}
such that, for every $x_u\in \cX$, $A(x_u)$ approximates at best the corresponding $u$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Validation set-up}
\asmodif{
To validate the results we can only rely on the available (few) sensors (at most $\perplexityinsert{numstations}$) and it does not suffice to make a split of training and testing in time because we observed that models tend to over-fit the locations in which they where trained. For this we need to perform a tripple Leave-One-Out procedure on the stations: one for testing, one for training super-learners and the final one for trainig each individual model (see \cref{fig:loodiagram} for a schematic view of the successive splitings).
\begin{enumerate}
	\item \textbf{Test split}: The first split is performed both in time and space. We take the first $\perplexityinsert{percentagetraintime}\%$ of the available times ($\perplexityinsert{numberoftraintimes}$ hours) for training $T_{\train}$ and the rest for testing $T_{\test}$. The Leave-One-Out is done on the station locations $r^\obs$ and associated pollution measurements $z$. As some stations are too near the border of the image, the available traffic information is not enough to add meaningfull information, for this reason even though we use all stations as information, we only take $\perplexityinsert{numstationstest}$\footnote{Stations away from borders are: \perplexityinsert{stationstest}.} for perfoming the testing Leave-One-Out. This means that we have to train in total $\perplexityinsert{numstationstest}$ different set of models associated with the different testing data splits $s\in S$, $\#S=\perplexityinsert{numstationstest}$, $I_s=\{i \in_{i \neq s} \{1, \dots m\}\}$
\begin{align}
	Y^{\test}_s(t) &= (z_s(t), r^\obs_s) \in \bR \times \bR^{2} \, \forall t \in T_{\test} \\
	X^{\train}_s(t) &= (z_{I_s}(t), r^\obs_{I_s}, q, T, w) \in \bR^{m-1} \times \bR^{2(m-1)} \times V \times \bR\times \bR^2 \, \forall t \in T_{\train}.	
\end{align}
	So the test error will be calculated as follws:
	$$e(u,A) \approx e^{\test}_{LOO}(Y^{\test}_s, A) = \frac{1}{\#T_{\test}}\sum_{t\in T_{\test}}\left(z_s-A(X^{\train}_s)(r^\obs_s)\right)^2$$
    \item \textbf{Super-learner train split}: For each training set we perform another Leave-One-Out to train each super-learner $(Y^{SL}_s, X^{SL}_s)$ both in $X^{\train}_s$.
    \item \textbf{Individual models train split}: For each training super-learner set we perform eone more Leave-One-Out to train each individual model under different circumstances avoiding this way the possibility of over-fitting: $(Y^{M}_s, X^{M}_s)$ both in $X^{SL}_s$.
\end{enumerate}
}{}

@@

The most usual approach to find the parameters is to resort to cross-validation, in which we search for
\ascomment{Check the equations, is it well written formally the belonging to the different LOO splits?}
\begin{equation}
\label{eq:fit-linear}
\min_{ \substack{\theta_1,\dots, \theta_n \in \Theta \\ \gamma_1,\dots, \gamma_n \in \Gamma}}
\sum_{ \substack{x\in X^{M} \\ (z, r)\in Y^{M}}}
\Vert z - \sum_{i=1}^n \ell(x, \theta_i) v(r, \gamma_i) \Vert^2_2,
\end{equation}
where $\Vert \cdot \Vert_2$ denotes the Euclidean norm. This norm can of course be replaced by any other lower semi-continuous loss function. From the optimal parameters $\theta_i^*$ and $\gamma_i^*$ of \eqref{eq:fit-linear}, we define
$$
A(x)(r) = \sum_{i=1}^n \ell(x, \theta_i^*) v(r, \gamma^*_i).
$$
Note that when using reduced modeling techniques, there is no optimization over the $\gamma_i$ since the $v_i$ are selected beforehand with specific techniques. A classical linear reconstruction map which we consider in our work is the so-called PBDW method (Parametrized-Background Data-Weak approach, see \cite{MPPY2015, BCDDPW2017, Mula2023}).

\paragraph{Nonlinear mappings:} In this case, $A$ is searched in a family of parametrized mappings of the form
$$
\cF \coloneqq \{ D(\theta): \cX \to V   \cond \theta \in \Theta  \},
$$
where the decoder function $D:\cX\to V$ is not necessarily linear. A common choice is to take $D$ as neural-network $\cN\cN$ with a given architecture, and trainable parameters $\theta \in \Theta\subseteq \bR^n$. By computing
\ascomment{Check the equations, is it well written formally the belonging to the different LOO splits?}
$$
\theta^* \in \argmin_{\theta \in \Theta}
\sum_{\substack{x\in X^{M} \\ (z, r)\in Y^{M}}}
\Vert z - \cN\cN(\theta)(r, x) \Vert^2_2,
$$
we then set
$$
A = \cN\cN(\theta^*).
$$
Note that the input and output spaces of the neural network are not finite dimensional spaces like in the classical definition of neural networks. Instead, our neural network should be understood as a neural operator. In section \ref{sec:concrete-methods} we provide a concrete example for our application.

@@

\asmodif{
Finally, another way to build a super-learner is by sequentially composing individual models $A_j$ together with transition functions $P_j$ and train them to correct the errors of previous ones so that 
$$
S_j(A_1, \dots, A_j) = P_j(\sigma_j^*) \circ A_j(\theta_j^*) \circ \dots \circ P_1(\sigma_1^*) \circ A_1(\theta_1^*)
$$
and $S=S_p$. At each step $j$ the target of each submodel is to correct the residuals $\tilde z_j=z - \cS_{j-1}(r, x)$ of previous steps, so $(z, r)\in Y^{M} \mapsto (\tilde z_j^{Y^{M}}, r) \in \tilde Y^{M}$. At the same time the information received from the pollution part of the input $x$ is also replaced by the last residual $x = (z, r^\obs, q, T, w) \in X^{M} \mapsto x_j^M = (\tilde z_j^{X^{M}}, r^\obs, q, T, w) \in \tilde X^{M}$ so the minimization problem in this step becomes
$$
\theta_j^* \in \underset{\theta_j \in \Theta_j}{\argmin}
\sum_{x_j^M, \tilde z_j^{Y^{M}}, r}
\Vert \tilde z_j^{Y^{M}} - A_j(\theta_j)(r, x_j^M)) \Vert^2_2.
$$
The transition maps $P_j$ are also trained to correct the residuals $\hat z_j=z - A_j(\theta_j^*)\circ\cS_{j-1}(r, x)$ of previous steps, so $(z, r)\in Y^{SL} \mapsto (\hat z_j^{Y^{SL}}, r) \in \hat Y^{SL}$ and $x = (z, r^\obs, q, T, w) \in X^{SL} \mapsto x_j^{SL} = (\tilde z_j^{X^{SL}}, r^\obs, q, T, w)  \in \hat X^{SL}$ so the minimization problem in this step becomes
$$
\sigma_j^* \in \underset{\sigma_j \in \Sigma_j}{\argmin}
\sum_{\hat z_j^{X^{SL}}, \hat z_j^{Y^{SL}}, r}
\Vert \hat z_j^{Y^{SL}} - P_j(\sigma_j)(\hat z_j^{X^{SL}}) \Vert^2_2.
$$
}{}

>>>>

@@

% Comments
\newcommand{\verify}[1]{{\color{blue} Verify: #1}}
\newcommand{\ascomment}[1]{{\color{teal} Agus: #1}}
\newcommand{\asmodif}[2]{{\color{teal} #1} {\sout{#2}}}
\newcommand{\om}[1]{\textcolor{blue}{#1}}

@@

Assuming that all the available information is given by an element $x$ from some abstract metric space $\cX$, and that $u$ belongs to some Banach space $V$ (of potentially infinite dimension, and with associated norm $\Vert\cdot\Vert$), our goal is thus to build a mapping $A:\cX\to V$ such that $A(x)$ approximates $u$ at best in the sense that $\Vert u - A(x)\Vert$ is as small as possible. Ideally, this has to hold for all possible configurations of the system. As we explain later on through mathematical formulas, building such an optimal map is not feasible in practice, so one is inevitably led to consider suboptimal maps $A$. In fact, it is often possible to resort to different techniques to build different reconstruction maps, each of them with its own virtues and drawbacks. This lead us to propose an approach based on ensemble super-learning in which the different reconstruction mappings do not directly compete against each other (see, e.g., \cite{Breiman1996, LPH2007, PL2010} for general references on super-learning). Instead, we make them collaborate with each other to enhance their respective strengths, and cope for their weaknesses.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pollution as a guiding example}
There are numerous applications in which one is confronted with the above state estimation problem. As a guiding example, we consider in this paper the real-time reconstruction of urban pollution fields. Beyond the relevance of such a task to limit environmental and health risks in the city, pollution state estimation is an excellent example where collaborative, super-learning methods are required. This is because the problem accumulates several difficulties that make the reconstruction challenging for most common reconstruction methods. Among the issues, we may mention:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Contributions and layout of the paper}
\paragraph{Contributions:} Our main contributions are (i) the construction of a very general ensemble super-learning method for real-time state estimation, (ii) the application to a non trivial example for urban pollution reconstruction and \asmodif{(iii) the construction of a dataset comprised of traffic Google Maps Screenshots that can be used for future studies and developements. \om{OLGA: I am fearful to say this because of possible Google copyright problems, Can we just say that we provide a code that can be used for future studies?}}. In our numerical experiments, we work with the inner city of Paris, which is a surface covering around $140\,\textrm{km}^2$. The pollutant that we consider is $\textrm{NO}_2$, mainly produced by vehicle emissions. We use real data from sensor measurements \footnote{Data has been extracted from Airparif database that can be found in  \url{https://data-airparif-asso.opendata.arcgis.com}.}, and traffic data from Google Maps. Compared to previous contributions and other existing reconstruction methods (see, e.g., \cite{MSM2009, TMPPB2013}), the use of such traffic data is rather novel. It gives a rough estimation of the spatial density of street traffic. This level of detail is in contrast to many existing approaches which only use time averages of traffic data. Another distinctive point of our approach is the use of graph descriptions of the city instead of working on a spatial domain of $\bR^2$ or $\bR^3$. This allows us to cope with large spatial domains, and also to define physical models through \emph{quantum graphs}, i.e., metric graphs  endowed with a differential operator acting on functions from a certain space (see \cite{BK2013} for details and references). The metric graph structure allows us to take the shape of the city into account, while the definition of differential operators enables to physically model the phenomenon of pollutant dispersion through the streets. It also leads to the definition of suitable and natural functional spaces to pose the problem. Of course, several physical models of different complexity could be considered. In this paper, we work with simple elliptic operators but the model could be refined by considering, for instance, advection-diffusion operators. %Despite the fact that we focus on urban air pollution, the main ideas of the strategy are general, in the sense that they can be taken as guidelines to adress other problems that can be modeled via quantum graphs.

@@

We assume that, from the unknown pollution field $u$, we are only given partial information which we will denote as $x$ (or $x_u$ whenever we need to emphasize the connection between $x$ and $u$). The data $x$ belongs to a metric space $\cX$, and it may contain several types of information about $u$ that can be of different nature (e.g., local sensor measurements and indirect information such as traffic or weather conditions). Assuming that $u$ belongs to a function space $V$ on the graph $\G$, our goal is to build a mapping
\begin{align*}
A: \cX &\to V \\
x &\mapsto A(x)
\end{align*}
such that, given $x_u\in \cX$, $A(x_u)$ approximates at best the true (unknown) $u$.

@@

We have worked with $m=\perplexityinsert{numstations}$ sensors functioning in the region of interest. As already brought up, their locations do not exactly match with the topology of the metric graph, therefore we project the position to the nearest node on the graph in a pre-processing step. This yields the observational nodes $\vv^\obs$ and coordinates $r^\obs$. As Figure \ref{fig:paris-stations} illustrates, the projected locations are very close to the exact locations given the global scale of the graph \asmodif{(the maximal discrepancy is $\perplexityinsert{MinDistNodeStation}$m, see \cref{fig:correlation})}{}. %Note however that the stations are originally located at different altitudes and since our graph is embedded only in $\bR^2$, we are not taking the effects of altitude into account.

@@

      \item \textbf{Raw data:} \asmodif{we made a script using the Selenium python library to automatically take screenshots of Paris\footnote{We tried in a first attempt to use the Google Maps Platform but as it required payment after one week of use we decided to code our own pipeline.} every $\perplexityinsert{screenshotperiod}$ minutes over an area of $\perplexityinsert{screenshotwidth} \times \perplexityinsert{screenshotheight}$ pixels with zoom $\perplexityinsert{zoom}$. An example of the raw  \textit{image} can be seen in \cref{fig:traffic-raw-data}. Note that city landmarks could not be removed before taking the screenshot neither by substracting a background image as each screenshot has slight variations rendering this approach impractical. Another issue is the absence of traffic data in the inner streets of the city. 

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Reconstruction benchmarks}
Our approach to reconstruct an unknown pollution field $u\in V$ from the partial data $x_u\in \cX$ is based on a supervised learning strategy involving super-learners. We thus assume that we have a database of $T$ observations, one for each time,
$$
X_T = \{x_1,\dots, x_T\} \subset \cX,
$$
each $x_k$ corresponding to partial observations of an unknown pollution field $u_k$ that took place in the past. Our goal is to use the database to build a reconstruction map
\begin{align*}
A: \cX &\to V \\
x &\mapsto A(x)
\end{align*}
such that, for every $x_u\in \cX$, $A(x_u)$ approximates at best the corresponding $u$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Validation set-up}
To validate the results we can only rely on the few available sensors ($m=\perplexityinsert{numstations}$) and it does not suffice to make a split of training and testing in time because we observed that models tend to over-fit the locations in which they where trained. For this we need to perform a tripple Leave-One-Out procedure on the stations: one for testing, one for training super-learners and the final one for trainig each individual model (see \cref{fig:loodiagram} for a schematic view of the successive splitings).
\begin{enumerate}
	\item \textbf{Test split}: The first split is performed both in time and space. We take the first $\perplexityinsert{percentagetraintime}\%$ of the available times ($\perplexityinsert{numberoftraintimes}$ hours) for training $T_{\train}$ and the rest for testing $T_{\test}$. The Leave-One-Out is done on the station locations $r^\obs$ and associated pollution measurements $z$. As some stations are too close to the border of the image, the available traffic information is not enough to add meaningfull information. For this reason even though we use all stations as information, we only take $\perplexityinsert{numstationstest}$ for perfoming the testing Leave-One-Out\footnote{Stations away from borders are: \perplexityinsert{stationstest}.}. This means that we have to train in total $\perplexityinsert{numstationstest}$ different sets of models associated with the different testing data splits $s\in S$, $\#S=\perplexityinsert{numstationstest}$, $I_s=\{i \in_{i \neq s} \{1, \dots m\}\}$ \om{[The idea is good. Something in the notation is maybe off. Some notation below was not introduced.]}
\begin{align}
	Y^{\test}_s(t) &= (z_s(t), r^\obs_s) \in \bR \times \bR^{2} \, \forall t \in T_{\test} \\
	X^{\train}_s(t) &= (z_{I_s}(t), r^\obs_{I_s}, q, T, w) \in \bR^{m-1} \times \bR^{2(m-1)} \times V \times \bR\times \bR^2 \, \forall t \in T_{\train}.	
\end{align}
	So the test error will be calculated as follws:
	$$e(u,A) \approx e^{\test}_{LOO}(Y^{\test}_s, A) = \frac{1}{\#T_{\test}}\sum_{t\in T_{\test}}\left(z_s-A(X^{\train}_s)(r^\obs_s)\right)^2$$
    \item \textbf{Super-learner train split}: For each training set we perform another Leave-One-Out to train each super-learner $(Y^{SL}_s, X^{SL}_s)$ both in $X^{\train}_s$.
    \item \textbf{Individual models train split}: For each training super-learner set we perform eone more Leave-One-Out to train each individual model under different circumstances avoiding this way the possibility of over-fitting: $(Y^{M}_s, X^{M}_s)$ both in $X^{SL}_s$.
\end{enumerate}

@@

The most usual approach to find the parameters is to resort to cross-validation, in which we search for
\ascomment{Check the equations, is it well written formally the belonging to the different LOO splits?} \om{[Which LOO do we use here?]}
\begin{equation}
\label{eq:fit-linear}
\min_{ \substack{\theta_1,\dots, \theta_n \in \Theta \\ \gamma_1,\dots, \gamma_n \in \Gamma}}
\sum_{ \substack{x\in X^{M} \\ (z, r)\in Y^{M}}}
\Vert z - \sum_{i=1}^n \ell(x, \theta_i) v(r, \gamma_i) \Vert^2_2,
\end{equation}
where $\Vert \cdot \Vert_2$ denotes the Euclidean norm. This norm can of course be replaced by any other lower semi-continuous loss function. From the optimal parameters $\theta_i^*$ and $\gamma_i^*$ of \eqref{eq:fit-linear}, we define
$$
A(x)(r) = \sum_{i=1}^n \ell(x, \theta_i^*) v(r, \gamma^*_i).
$$
Note that when using reduced modeling techniques, there is no optimization over the $\gamma_i$ since the $v_i$ are selected beforehand with specific techniques. A classical linear reconstruction map which we consider in our work is the so-called PBDW method (Parametrized-Background Data-Weak approach, see \cite{MPPY2015, BCDDPW2017, Mula2023}).

\paragraph{Nonlinear mappings:} In this case, $A$ is searched in a family of parametrized mappings of the form
$$
\cF \coloneqq \{ D(\theta): \cX \to V   \cond \theta \in \Theta  \},
$$
where the decoder function $D:\cX\to V$ is not necessarily linear. A common choice is to take $D$ as neural-network $\cN\cN$ with a given architecture, and trainable parameters $\theta \in \Theta\subseteq \bR^n$. By computing
\ascomment{Check the equations, is it well written formally the belonging to the different LOO splits?} \om{[What LOO to use?]}
$$
\theta^* \in \argmin_{\theta \in \Theta}
\sum_{\substack{x\in X^{M} \\ (z, r)\in Y^{M}}}
\Vert z - \cN\cN(\theta)(r, x) \Vert^2_2,
$$
we then set
$$
A = \cN\cN(\theta^*).
$$
Note that the input and output spaces of the neural network are not finite dimensional spaces like in the classical definition of neural networks. Instead, our neural network should be understood as a neural operator. In section \ref{sec:concrete-methods} we provide a concrete example for our application.

@@

\asmodif{
Finally, another way to build a super-learner is by sequentially composing individual models $A_j$ together with transition functions $P_j$ and train them to correct the errors of previous ones so that \om{[It is $A_j(x)$ and not $A_j(\theta)$. I guess you mean to discuss the case when $A_j = \cN\cN(\theta)?$]}
$$
S_j(A_1, \dots, A_j) = P_j(\sigma_j^*) \circ A_j(\theta_j^*) \circ \dots \circ P_1(\sigma_1^*) \circ A_1(\theta_1^*)
$$
and $S=S_p$. At each step $j$ the target of each submodel is to correct the residuals $\tilde z_j=z - \cS_{j-1}(r, x)$ of previous steps, so $(z, r)\in Y^{M} \mapsto (\tilde z_j^{Y^{M}}, r) \in \tilde Y^{M}$. At the same time the information received from the pollution part of the input $x$ is also replaced by the last residual $x = (z, r^\obs, q, T, w) \in X^{M} \mapsto x_j^M = (\tilde z_j^{X^{M}}, r^\obs, q, T, w) \in \tilde X^{M}$ so the minimization problem in this step becomes
$$
\theta_j^* \in \underset{\theta_j \in \Theta_j}{\argmin}
\sum_{x_j^M, \tilde z_j^{Y^{M}}, r}
\Vert \tilde z_j^{Y^{M}} - A_j(\theta_j)(r, x_j^M)) \Vert^2_2.
$$
The transition maps $P_j$ are also trained to correct the residuals $\hat z_j=z - A_j(\theta_j^*)\circ\cS_{j-1}(r, x)$ of previous steps, so $(z, r)\in Y^{SL} \mapsto (\hat z_j^{Y^{SL}}, r) \in \hat Y^{SL}$ and $x = (z, r^\obs, q, T, w) \in X^{SL} \mapsto x_j^{SL} = (\tilde z_j^{X^{SL}}, r^\obs, q, T, w)  \in \hat X^{SL}$ so the minimization problem in this step becomes
$$
\sigma_j^* \in \underset{\sigma_j \in \Sigma_j}{\argmin}
\sum_{\hat z_j^{X^{SL}}, \hat z_j^{Y^{SL}}, r}
\Vert \hat z_j^{Y^{SL}} - P_j(\sigma_j)(\hat z_j^{X^{SL}}) \Vert^2_2.
$$
}{}
